### 2017-12-27 icde/revision/sec-incAlg.tex

\vspace{-1ex}
\begin{small}
\begin{equation}\label{eq-inc-pop}
Pop_c^+(v) = Pop_c(v) {e^{\sigma (T^+_0-T_0)}} + \sum_{(u,v)\in \Delta E^c} {e^{\sigma (T^+_0-T_u)}},
\end{equation}
\end{small}
\noindent
where $Pop_c(v)$ (resp. $Pop_c^+(v)$) is the popularity of node $v$ on $G^c$ (resp. $G^{c,+}$), and
 $T_0$ (resp. $T^+_0$) is the current time on $G^c$ (resp. $G^{c,+}$).
%
By Eq.~(\ref{eq-inc-pop}), it is easy to see that it takes $O($ $|V^c|+|\Delta V^c|+|\Delta E^c|)$ time to update the popularity.
%This further shows that Eq.~(\ref{eq-inc-pop}) is a desired solution for popularity maintenance.

@@

\begin{proofSketch}
We prove that for each edge $(u,v)$ in the block-wise graph of $G^+$, node $u$ comes before $v$ in $O^+$, and the conclusion follows by the definition of topological order.
\end{proofSketch}

@@

%%%%%%%%%%%%%%%%%%%%%Algorithm
\begin{figure}[tb!]
%\vspace{2ex}
\begin{center}
{\small
\begin{minipage}{3.36in}
\myhrule \vspace{-1.5ex}
\mat{0ex}{
%%%%%%%%%%%%%%%%%%%
{\sl Input:\/} \= An update $\Delta$ = $\Delta V\cup\Delta E$, TWPageRank vector $PR$ of $G$,\\
\hspace{5ex}   and the  topological order $O$ of the block-wise graph $G'$.\\
{\sl Output:\/} TWPageRank vector $PR^+$ of the updated graph $G^+$. \\
\\
\bcc \hspace{1.5ex}\=  $G_C'$ := the block-wise graph of $G_C$; \\
%\ \  $E_{CB}'$ := edges from $G_C'$ to $G'$\\
\icc\> $\Delta O$ := topological order of $G_C'$; \ \ $O^+$ := $\Delta O/O$; \\
\icc\> label \sccs of $G_C$ as $C$, \sccs of $G$ with outgoing edges having \\ \hspace{2.5ex}    weight changes as $B$, and the remaining \sccs of $G$ as $A$;\\
\icc\>  \For each node $v'$ following $O^+$ \Do\\
\icc\>\hspace{2.5ex}\= $scc$ := the corresponding \scc of $v'$; \\
%\icc\>\>\If impact weight of $(v,w)$ is changed where $v\in scc$ \Then \\
%\icc\>\>\hspace{3ex}\= label $scc$ as $B$;\\
%\icc\>\>\> label SCC $w'$ as $B$ such that $(v',w')\in E'$; \\
\icc\>\> \If $scc$ is labeled as $C$ \Then \\
\icc\>\>\hspace{3ex}\= update $PR^+(v)$ ($v\in scc$) following algorithm~\twprscc; \\
\icc\>\>\> label \scc $w'$ as $B$ with $w'\in G'$ and $(v', w')\in E^+{'}$;\\
\icc\>\> \Else \If $scc$ is labeled as $B$ \Then \\
\icc\>\>\> update $PR^+(v)$ where $v\in scc$ with Eq.~(\ref{eq-inc-prscc}) until the \\ \hspace{8ex}  sum of TWPageRank score changes is less than $\epsilon\cdot \frac{|scc|}{|V^+|}$; \\
\icc\>\>\> label \scc $w'$ as $B$ with $(v',w')\in E'$;\\
\icc\>\> \Else $PR^+(v)$:=$PR(v)\cdot {n}/{n^+}$ where $v\in scc$; \\
\icc\> \Return $PR^+$.
}
\vspace{-2.5ex} \myhrule
\end{minipage}
}
\end{center}
\vspace{-1ex}
\caption{\small Algorithm~\inctwprscc for incremental TWPageRank} \label{alg-inctwprscc}
\vspace{-3ex}
\end{figure}
%%%%%%%%%%%%Algorithm

@@

\begin{proofSketch}
Assume a topological order $v_1'/\dots/v_{l}'$ of the block-wise graph $G^+{'}$ where $l=|O^+|$. It suffices to prove by induction that the sum of changes of $PR^+(v)$ ($v\in scc_k$) is no more than $\epsilon |scc_k|/|V^+|$ for $scc_k$ of $v_k'$ ($k\in [1,l]$).
%The conclusion follows combining Lemma~\ref{prop-prscc}
%(see \cite{SARank-full} for details).
\end{proofSketch}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{table}[tb!]
%\vspace{-2ex}
\begin{center}
\caption{\small Statistics of affected/unaffected areas given a yearly update, \ie articles of 2011 on \aan and 2015 on \aminer and \magdata, respectively.}
\label{tab-inc}
%\begin{small}
%\vspace{-.5ex}
\eat{
\begin{tabular}{|c|c|c|}
\hline
{\bf Graphs} & $|V_A|$\hspace{2ex}$|V_B|$\hspace{3ex}$|V_C|$ & $|E_A|$\hspace{2ex}$|E_{AB}|$\hspace{2ex}$|E_B|$\hspace{2ex}$|E_{CB}|$\hspace{2ex}$|E_C|$ \\
\hline \hline
% citation graphs
\aan & $46.9\%$\ $47.3\%$\ $5.8\%$ & \ $2.9\%$\ $25.9\%$\ $60.5\%$\ $10.4\%$ \hspace{1ex} $0.3\%$ \\
\aminer & $81.4\%$ \hspace{1ex} $10.7\%$ \hspace{1ex} $7.8\%$ & $18.0\%$ \hspace{1ex} $53.2\%$ \hspace{1ex} $25.1\%$ \hspace{1ex} \ $2.3\%$ \hspace{1ex} $1.4\%$ \\
\magdata & $69.5\%$ \hspace{1ex} $25.9\%$ \hspace{1ex} $4.5\%$ & \ $1.0\%$ \hspace{1ex} $27.4\%$ \hspace{1ex} $64.5\%$ \hspace{1ex} \ $7.0\%$ \hspace{1ex} $0.1\%$ \\ \hline
% venue graphs
\aan & \ $2.1\%$ \hspace{1ex} $92.0\%$ \hspace{1ex} $5.8\%$ & \ $1.0\%$ \hspace{1ex} \ $1.0\%$ \hspace{1ex} $88.8\%$ \hspace{1ex} $10.0\%$ \hspace{1ex} $0.2\%$ \\
\aminer & $45.8\%$ \hspace{1ex} $47.7\%$ \hspace{1ex} $6.4\%$ & \ $0.0\%$ \hspace{1ex} \ $3.2\%$ \hspace{1ex} $95.4\%$ \hspace{1ex} \ $1.0\%$ \hspace{1ex} $0.1\%$ \\
\magdata & $12.4\%$ \hspace{1ex} $84.6\%$ \hspace{1ex} $3.0\%$ & \ $0.0\%$ \hspace{1ex} \ $0.1\%$ \hspace{1ex} $92.6\%$ \hspace{1ex} \ $7.1\%$ \hspace{1ex} $0.1\%$ \\
 \hline
\end{tabular}
}
\begin{tabular}{|c|c c c|c c c|}
\hline
 & \multicolumn{3}{c|}{\bf Citation graphs on}   & \multicolumn{3}{c|}{\bf Venue graphs on}    \\
\raisebox{1ex}[0pt]{\bf Statis.} & \aan & \aminer & \magdata & \aan & \aminer & \magdata \\
\hline \hline
$|V_A|$ & 47.4\% & 52.3\% & 69.2\% & 2.1\% & 8.7\% & 12.4\% \\
$|V_B|$ & 46.8\% & 40.0\% & 26.3\% & 92.0\% & 84.8\% & 84.6\% \\
$|V_C|$ & \ 5.8\% & \ 7.8\% & \ 4.5\% & \ 5.8\% & \ 6.4\% & \ 3.0\% \\ \hline
% venue graphs
$|E_A|$ & \ 3.0\% & 2.4\% & \ 0.9\% & \ 0.0\% & \ 0.0\% & \ 0.0\% \\
$|E_{AB}|$ & 26.5\% & 30.2\% & 26.6\% & \ 1.2\% & \ 0.2\% & \ 0.1\% \\
$|E_B|$ & 59.8\% & 59.3\% & 65.5\% & 88.6\% & 92.3\% & 92.6\% \\
$|E_{CB}|$ & 10.4\% & \ 7.2\% & \ 7.0\% & 10.0\% & \ 7.3\% & \ 7.1\% \\
$|E_C|$ & \ 0.3\% & \ 0.9\% & \ 0.1\% & \ 0.2\% & \ 0.2\% & \ 0.1\% \\ \hline
\end{tabular}
%\end{small}
\end{center}
\vspace{-5ex}
\end{table}
%%%%%%%%%%%%%%%%%%%

\stitle{Time \& space complexity analyses of the incremental algorithm}.
By the analyses above, the time complexity of \incensemble is the same as \batensemble, except that \incensemble saves $O(|E^c_A\cup E^c_{AB}|)$ and $O(|E^v_A\cup E^v_{AB}|)$ time on the updated citation and venue graphs. And its space complexity is also the same as \batensemble, except that it uses $(|V^c\cup \Delta V^c|+|V^v\cup\Delta V^v|)$ extra space to store the affected/unaffected areas and $(|E^c\cup \Delta E^c|+|E^v\cup \Delta E^v|)$ extra space to store the original edge weights before update.

Despite of its similar time complexity to \batensemble, algorithm \incensemble typically achieves a substantial efficiency improvement over \batensemble, according to our statistics of affected/unaffected areas shown in Table~II.
%
(a) It saves $O(|V^c|+|E^c|)$ and $O(|V^v|+|E^v|)$ time when maintaining \sccs and the topological order based on $\Delta^c$ and $\Delta^v$ only, where ($|V^c|$, $|E^c|$, $|V^v|$, $|E^v|$) are more than (92\%, 89\%, 93\%, 89\%) of ($|V^{c,+}|$, $|E^{c,+}|$, $|V^{v,+}|$, $|E^{v,+}|$) on all tested graphs;
(b) It saves $O(|E^c_A \cup E^c_{AB}|)$ time when updating scores on $V^c$, where edges in $E^c_A\cup E^c_{AB}$ account for more than 28\% of total edges;
(c) It saves $O(|E^c|)$ time when computing popularity of articles, which accounts for more than 89\% of $|E^{c,+}|$;
And, finally, (d) It is likely to compute TWPageRank scores on $V^c_B$ and $V^v_B$ with less iterations.

>>>>

\vspace{-1ex}
\begin{small}
\begin{equation}\label{eq-inc-pop}
Pop_c^+(v) = Pop_c(v) {e^{\sigma (T^+_0-T_0)}} + \sum_{(u,v)\in \Delta E^c} {e^{\sigma (T^+_0-T_u)}},
\end{equation}
\end{small}
%
\noindent where $Pop_c(v)$ (resp. $Pop_c^+(v)$) is the popularity of node $v$ on $G^c$ (resp. $G^{c,+}$), and
$T_0$ (resp. $T^+_0$) is the current time on $G^c$ (resp. $G^{c,+}$).
%
By Eq.~(\ref{eq-inc-pop}), it is easy to see that it takes $O($ $|V^c|+|\Delta V^c|+|\Delta E^c|)$ time to update the popularity.
%This further shows that Eq.~(\ref{eq-inc-pop}) is a desired solution for popularity maintenance.

@@

\eat{
\begin{proofSketch}
We prove that for each edge $(u,v)$ in the block-wise graph of $G^+$, node $u$ comes before $v$ in $O^+$, and the conclusion follows by the definition of topological order.
\end{proofSketch}
}

@@

%%%%%%%%%%%%%%%%%%%%%Algorithm
\begin{figure}[tb!]
%\vspace{2ex}
\begin{center}
{\small
\begin{minipage}{3.36in}
\myhrule \vspace{-1.5ex}
\mat{0ex}{
%%%%%%%%%%%%%%%%%%%
{\sl Input:\/} \= An update $\Delta$ = $\Delta V\cup\Delta E$, TWPageRank vector $PR$ of $G$,\\
\hspace{5ex}   and the  topological order $O$ of the block-wise graph $G'$.\\
{\sl Output:\/} TWPageRank vector $PR^+$ of the updated graph $G^+$. \\
\bcc \hspace{1.5ex}\=  $G_C'$ := the block-wise graph of $G_C$; \\
%\ \  $E_{CB}'$ := edges from $G_C'$ to $G'$\\
\icc\> $\Delta O$ := topological order of $G_C'$; \ \ $O^+$ := $\Delta O/O$; \\
\icc\> label \sccs of $G_C$ as $C$, \sccs of $G$ with outgoing edges having \\ \hspace{2.5ex}    weight changes as $B$, and the remaining \sccs of $G$ as $A$;\\
\icc\>  \For each node $v'$ following $O^+$ \Do\\
\icc\>\hspace{2.5ex}\= $scc$ := the corresponding \scc of $v'$; \\
%\icc\>\>\If impact weight of $(v,w)$ is changed where $v\in scc$ \Then \\
%\icc\>\>\hspace{3ex}\= label $scc$ as $B$;\\
%\icc\>\>\> label SCC $w'$ as $B$ such that $(v',w')\in E'$; \\
\icc\>\> \If $scc$ is labeled as $C$ \Then \\
\icc\>\>\hspace{3ex}\= update $PR^+(v)$ ($v\in scc$) following algorithm~\twprscc; \\
\icc\>\>\> label \scc $w'$ as $B$ with $w'\in G'$ and $(v', w')\in E^+{'}$;\\
\icc\>\> \Else \If $scc$ is labeled as $B$ \Then \\
\icc\>\>\> update $PR^+(v)$ where $v\in scc$ with Eq.~(\ref{eq-inc-prscc}) until the \\ \hspace{8ex}  sum of TWPageRank score changes is less than $\epsilon\cdot \frac{|scc|}{|V^+|}$; \\
\icc\>\>\> label \scc $w'$ as $B$ with $(v',w')\in E'$;\\
\icc\>\> \Else $PR^+(v)$:=$PR(v)\cdot {n}/{n^+}$ where $v\in scc$; \\
\icc\> \Return $PR^+$.
}
\vspace{-2.5ex} \myhrule
\end{minipage}
}
\end{center}
\vspace{-1ex}
\caption{\small Algorithm~\inctwprscc for incremental TWPageRank} \label{alg-inctwprscc}
\vspace{-3ex}
\end{figure}
%%%%%%%%%%%%Algorithm

@@

\eat{
\begin{proofSketch}
Assume a topological order $v_1'/\dots/v_{l}'$ of the block-wise graph $G^+{'}$ where $l=|O^+|$. It suffices to prove by induction that the sum of changes of $PR^+(v)$ ($v\in scc_k$) is no more than $\epsilon |scc_k|/|V^+|$ for $scc_k$ of $v_k'$ ($k\in [1,l]$).
%The conclusion follows combining Lemma~\ref{prop-prscc}
%(see \cite{SARank-full} for details).
\end{proofSketch}
}

@@

\eat{  %% time & space complexity
\stitle{Time \& space complexity analyses of the incremental algorithm}.
By the analyses above, the time complexity of \incensemble is the same as \batensemble, except that \incensemble saves $O(|E^c_A\cup E^c_{AB}|)$ and $O(|E^v_A\cup E^v_{AB}|)$ time on the updated citation and venue graphs. And its space complexity is also the same as \batensemble, except that it uses $(|V^c\cup \Delta V^c|+|V^v\cup\Delta V^v|)$ extra space to store the affected/unaffected areas and $(|E^c\cup \Delta E^c|+|E^v\cup \Delta E^v|)$ extra space to store the original edge weights before update.
} %% eat

\stitle{Time complexity analysis of the incremental algorithm}.
By the analyses above, the time complexity of \incensemble is the same as \batensemble, except that \incensemble saves $O(|E^c_A\cup E^c_{AB}|)$ and $O(|E^v_A\cup E^v_{AB}|)$ time on the updated citation and venue graphs at an extra space cost for the affected/unaffected areas and the original edge weights.

Despite of its similar time complexity to \batensemble, algorithm \incensemble typically achieves a substantial efficiency improvement over \batensemble, according to our statistics of affected/unaffected areas given a yearly update, \ie articles of 2011 on \aan and 2015 on \aminer and \magdata, respectively, shown in Table~II.
%
(a) It saves $O(|V^c|+|E^c|)$ and $O(|V^v|+|E^v|)$ time when maintaining \sccs and the topological order based on $\Delta^c$ and $\Delta^v$ only, where ($|V^c|$, $|E^c|$, $|V^v|$, $|E^v|$) are more than (92\%, 89\%, 93\%, 89\%) of ($|V^{c,+}|$, $|E^{c,+}|$, $|V^{v,+}|$, $|E^{v,+}|$) on all tested graphs;
(b) It saves $O(|E^c_A \cup E^c_{AB}|)$ time when updating scores on $V^c$, where edges in $E^c_A\cup E^c_{AB}$ account for more than 28\% of total edges;
(c) It saves $O(|E^c|)$ time when computing popularity of articles, which accounts for more than 89\% of $|E^{c,+}|$;
And, finally, (d) It is likely to compute TWPageRank scores on $V^c_B$ and $V^v_B$ with less iterations.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{table}[tb!]
%\vspace{-2ex}
\begin{center}
\caption{\small Statistics of affected/unaffected areas}
\label{tab-inc}
%\begin{small}
%\vspace{-.5ex}
\eat{
\begin{tabular}{|c|c|c|}
\hline
{\bf Graphs} & $|V_A|$\hspace{2ex}$|V_B|$\hspace{3ex}$|V_C|$ & $|E_A|$\hspace{2ex}$|E_{AB}|$\hspace{2ex}$|E_B|$\hspace{2ex}$|E_{CB}|$\hspace{2ex}$|E_C|$ \\
\hline \hline
% citation graphs
\aan & $46.9\%$\ $47.3\%$\ $5.8\%$ & \ $2.9\%$\ $25.9\%$\ $60.5\%$\ $10.4\%$ \hspace{1ex} $0.3\%$ \\
\aminer & $81.4\%$ \hspace{1ex} $10.7\%$ \hspace{1ex} $7.8\%$ & $18.0\%$ \hspace{1ex} $53.2\%$ \hspace{1ex} $25.1\%$ \hspace{1ex} \ $2.3\%$ \hspace{1ex} $1.4\%$ \\
\magdata & $69.5\%$ \hspace{1ex} $25.9\%$ \hspace{1ex} $4.5\%$ & \ $1.0\%$ \hspace{1ex} $27.4\%$ \hspace{1ex} $64.5\%$ \hspace{1ex} \ $7.0\%$ \hspace{1ex} $0.1\%$ \\ \hline
% venue graphs
\aan & \ $2.1\%$ \hspace{1ex} $92.0\%$ \hspace{1ex} $5.8\%$ & \ $1.0\%$ \hspace{1ex} \ $1.0\%$ \hspace{1ex} $88.8\%$ \hspace{1ex} $10.0\%$ \hspace{1ex} $0.2\%$ \\
\aminer & $45.8\%$ \hspace{1ex} $47.7\%$ \hspace{1ex} $6.4\%$ & \ $0.0\%$ \hspace{1ex} \ $3.2\%$ \hspace{1ex} $95.4\%$ \hspace{1ex} \ $1.0\%$ \hspace{1ex} $0.1\%$ \\
\magdata & $12.4\%$ \hspace{1ex} $84.6\%$ \hspace{1ex} $3.0\%$ & \ $0.0\%$ \hspace{1ex} \ $0.1\%$ \hspace{1ex} $92.6\%$ \hspace{1ex} \ $7.1\%$ \hspace{1ex} $0.1\%$ \\
 \hline
\end{tabular}
}
\begin{tabular}{|c|c c c|c c c|}
\hline
 & \multicolumn{3}{c|}{\bf Citation graphs on}   & \multicolumn{3}{c|}{\bf Venue graphs on}    \\
\raisebox{1ex}[0pt]{\bf Statis.} & \aan & \aminer & \magdata & \aan & \aminer & \magdata \\
\hline \hline
$|V_A|$ & 47.4\% & 52.3\% & 69.2\% & 2.1\% & 8.7\% & 12.4\% \\
$|V_B|$ & 46.8\% & 40.0\% & 26.3\% & 92.0\% & 84.8\% & 84.6\% \\
$|V_C|$ & \ 5.8\% & \ 7.8\% & \ 4.5\% & \ 5.8\% & \ 6.4\% & \ 3.0\% \\ \hline
% venue graphs
$|E_A|$ & \ 3.0\% & 2.4\% & \ 0.9\% & \ 0.0\% & \ 0.0\% & \ 0.0\% \\
$|E_{AB}|$ & 26.5\% & 30.2\% & 26.6\% & \ 1.2\% & \ 0.2\% & \ 0.1\% \\
$|E_B|$ & 59.8\% & 59.3\% & 65.5\% & 88.6\% & 92.3\% & 92.6\% \\
$|E_{CB}|$ & 10.4\% & \ 7.2\% & \ 7.0\% & 10.0\% & \ 7.3\% & \ 7.1\% \\
$|E_C|$ & \ 0.3\% & \ 0.9\% & \ 0.1\% & \ 0.2\% & \ 0.2\% & \ 0.1\% \\ \hline
\end{tabular}
%\end{small}
\end{center}
\vspace{-5ex}
\end{table}
%%%%%%%%%%%%%%%%%%%

### 2017-12-27 icde/revision/sec-intro.tex

Query independent ranking of scholarly articles has drawn significant attentions from both academia~\cite{Garfield471,Hirsch15112005,Liang16AAAI,Jiang12-MRank,Waltman2014,Wang16TIST,Ng11KDD,Li08TSRanking,
Wang13AAAI,sayyadi09,WalkerXKM07,TanLMGSW16} and industry~\cite{g-scholar,Sinha15:MAG,sem-scholar}.
Generally speaking, a ranking is {\em a function that assigns each item a numerical score}. Query independent ranking aims to give a static ranking based on the scholarly  data only, and is independent of how well articles match a specific query. Such a ranking plays a key role in literature recommendation systems, especially in the {\em cold start} scenario.

@@

\sstab(1) We first  propose a \underline{S}cholarly \underline{A}rticle \underline{Rank}ing model, referred to as \ensemblerank, by assembling the importance of three classes of entities (articles, venues and authors) for scholarly article ranking (Section \ref{sec-model}).
%
The importance is a combination of {\em prestige} and {\em popularity} to capture the evolving nature of entities.
%
To compute the prestige of articles and venues, we propose a novel {\em Time-Weighted PageRank} with a time decaying factor based on the citation statistics (instead of simple exponential decay), and the prestige of authors is the average prestige of all their published articles.
%
The popularity of an article is the sum of all its citation freshness (how close to the current year), while the one of venues and authors is the average popularity of their associated articles.
%
%Observe that (a), intuitively, prestige favors articles with many citations soon after their publication, and popularity favors those with recent citations, and (b) both prestige and popularity capture the evolving nature of entities.
%
To our knowledge, the Time-Weighted PageRank is among the first to \markedb{use citation statistics to incorporate the diverse citation patterns of individual articles for scholarly article ranking.}
%and the long-term bias caused by the dynamic nature of data

\sstab(2)  We then develop  a batch algorithm for scholarly article ranking (Section \ref{sec-alg}), in which we propose a block-wise method for Time-Weighted PageRank \markedb{and show its advantage in terms of an efficiency analysis based on citation characteristics of scholarly articles.}
%in which we propose a block-wise method for Time-Weighted PageRank in terms of an analysis of the citation characteristics of scholarly articles.

@@

All the detailed proofs can be found in \cite{SARank-full}.

>>>>

Query independent ranking of scholarly articles has drawn significant attentions from both academia~\cite{Garfield471,Hirsch15112005,Liang16AAAI,Jiang12-MRank,Waltman2014,Wang16TIST,Ng11KDD,Li08TSRanking,
Wang13AAAI,sayyadi09,WalkerXKM07} and industry~\cite{g-scholar,Sinha15:MAG,sem-scholar}.
Generally speaking, a ranking is {\em a function that assigns each item a numerical score}. Query independent ranking aims to give a static ranking based on the scholarly  data only, and is independent of how well articles match a specific query. Such a ranking plays a key role in literature recommendation systems, especially in the {\em cold start} scenario.
%,TanLMGSW16

@@

\sstab(1) We first  propose a \underline{S}cholarly \underline{A}rticle \underline{Rank}ing model, referred to as \ensemblerank, by assembling the importance of three classes of entities (articles, venues and authors) for scholarly article ranking (Section \ref{sec-model}).
%
The importance is a combination of {\em prestige} and {\em popularity} to capture the evolving nature of entities.
%
To compute the prestige of articles and venues, we propose a novel {\em Time-Weighted PageRank} with a time decaying factor based on the citation statistics (instead of simple exponential decay), and the prestige of authors is the average prestige of all their published articles.
%
The popularity of an article is the sum of all its citation freshness (how close to the current year), while the one of venues and authors is the average popularity of their associated articles.
%
%Observe that (a), intuitively, prestige favors articles with many citations soon after their publication, and popularity favors those with recent citations, and (b) both prestige and popularity capture the evolving nature of entities.
%
To our knowledge, the Time-Weighted PageRank is among the first to incorporate the diverse citation patterns of individual articles \markedb{and exploit citation statistics for scholarly article ranking.}
%and the long-term bias caused by the dynamic nature of data

\sstab(2)  We then develop  a batch algorithm for scholarly article ranking (Section \ref{sec-alg}), in which we propose a block-wise method for Time-Weighted PageRank \markedb{and show its efficiency advantage in terms of an analysis of the citation characteristics and a specific structural property of scholarly graphs.}
%in which we propose a block-wise method for Time-Weighted PageRank in terms of an analysis of the citation characteristics of scholarly articles.

@@

%All the detailed proofs can be found in \cite{SARank-full}.
All the proofs can be found in \cite{SARank-full}.

### 2017-12-27 icde/revision/sec-model.tex

\stitle{Time-Weighted PageRank (TWPageRank)}. Most previous work simply exploits temporal information in the form of exponential decay~\cite{Li08TSRanking,Wang13AAAI,sayyadi09,WalkerXKM07}. We rethink the usage of time information in terms of the impacts of scholarly articles.
Recall that articles are categorized  into six citation patterns featured by the time when the articles reach their citation peaks~\cite{Chakraborty15}: (a) {\em PeakInit} with a single citation-count peak in the first five years (but not the first year) after publication, (b) {\em PeakMul} with distinct multiple peaks, (c) {\em PeakLate} with a single peak in at least five years   (but not the last year) after publication, (d) {\em MonDec} with monotonically decreasing citations, (e) {\em MonIncr} with monotonically increasing citations, and, (f) {\em Other} for articles whose average numbers of citations per year are less than 1. Though the number of citations is an indicator of the impact of an article~\cite{WangSB13,Garfield471}, its impact is time-dependent and is not simply in the form of exponential decay.
In general, {\em the impact of an article tends to decay with time after the peak time only}. That is, the impacts of articles directly decay with time only for those in {\em MonDec}, and decay with time after the peak time for those in {\em PeakInit}, {\em PeakLate} and {\em PeakMul}, and do not decay for ones in {\em MonIncr} (which is rare).
%Otherwise, its impact is fixed as a constant number. %, since we argue that the increment of its citations during this period is mainly due to the increase of its popularity.
Also observe that {\em each individual article has its own peak time} as articles may reach their citation peaks in different patterns and time.
%using the peak year in Fig.~\ref{fig-citation} is not appropriate for all articles. On the contrary, we compute a peak year for each article.

@@

\vspace{-1ex}
\begin{small}
\begin{equation} \label{eq-infl-weights}
w(u,v)  =  \begin{cases}  \hspace{7ex} 1 & T_u <  Peak_v \\
  e^{\sigma(T_u-Peak_v)} & T_u \geq Peak_v,
\end{cases}
\end{equation}
\end{small}
%
\noindent where $T_u$ is the time of node $u$, $Peak_v$ is the peak time of node $v$ after which the impact weights of edges to $v$ decay with time, and $\sigma$ is a negative number controlling the decaying speed of the impacts.
By default, Eq.~(\ref{eq-infl-weights}) uses years as its time granularity. Note that the time decaying factor $\sigma$ is introduced to provide flexibility for TWPageRank in various applications, and its value is typically within a small interval, \eg $[-2,0]$, such that $w(u,v)$ does not decay when $\sigma=0$ and already decays more than a half per year when $\sigma=-1$.
For the sake of completeness, we further set $w(u,v)$ to $0$ if there does not exist an edge from $u$ to $v$ in the graph.

@@

\begin{figure}[tb!]
\centering
%\includegraphics[scale=0.15]{fig/framework.eps}
\includegraphics[scale=0.175]{fig/framework-lite-2.eps}
\vspace{-1ex}
\caption{\small Ranking model \ensemblerank} \label{fig-rankmodel}
\vspace{-3ex}
\end{figure}

@@

%However, the resulting author citation graph to compute the prestige is typically too large to handle.
\markedb{To do this, an author citation graph needs to be constructed such that (a) a node represents an author, and (b) a direct edge $(s,t)$ denotes that there exist articles of author $s$ citing articles of author $t$. It is not hard to image that the number of edges in the author citation graph is much larger than the number in the citation graph, which reaches to 7.12  billion on the largest \magdata (\ie the memory cost of storage only is 57GB). It is computationally expensive to compute prestige of authors with TWPageRank on that graph.}
Hence, we evaluate the prestige of an author, by using the average prestige of all articles published by the author. Similar to the venue component, the popularity of an author is also defined as the average popularity of her/his published articles. Finally, the prestige and popularity are combined to derive the importance in the same way as the citation component.

@@

\stitle{Ranking with importance assembling}. The aforementioned importance is finally assembled to produce the final ranking, as illustrated in Fig.~\ref{fig-rankmodel}. Before assembling, each component is properly scaled such that the average importance scores of citations, venues and authors are the same.  Let the scaled importance scores of article $v$ be $R_c(v)$, $R_v(v)$, and $R_a(v)$ from the citation, venue and author components, respectively.

The final ranking score $R(v)$ of an article $v$ is aggregated as follows:

>>>>

\stitle{Time-Weighted PageRank (TWPageRank)}. Most previous work simply exploits temporal information in the form of exponential decay~\cite{Li08TSRanking,Wang13AAAI,sayyadi09,WalkerXKM07}. We rethink the usage of time information in terms of the impacts of scholarly articles.
Recall that articles are categorized  into six citation patterns featured by the time when the articles reach their citation peaks~\cite{Chakraborty15}: (a) {\em PeakInit} with a single citation-count peak in the first five years (but not the first year) after publication, (b) {\em PeakMul} with distinct multiple peaks, (c) {\em PeakLate} with a single peak in at least five years   (but not the last year) after publication, (d) {\em MonDec} with monotonically decreasing citations, (e) {\em MonIncr} with monotonically increasing citations, and, (f) {\em Other} for articles whose average numbers of citations per year are less than 1. Though the number of citations is an indicator of the impact of an article~\cite{WangSB13,Garfield471}, its impact is time-dependent and is not simply in the form of exponential decay.
% In general,
\markedb{Inspired by these citation patterns,} {\em the impact of an article tends to decay with time after the peak time only}~\cite{WangSB13}. That is, the impacts of articles directly decay with time only for those in {\em MonDec}, and decay with time after the peak time for those in {\em PeakInit}, {\em PeakLate} and {\em PeakMul}, and do not decay for ones in {\em MonIncr} (which is rare).
%Otherwise, its impact is fixed as a constant number. %, since we argue that the increment of its citations during this period is mainly due to the increase of its popularity.
Also observe that {\em each individual article has its own peak time} as articles may reach their citation peaks in different patterns and time.
%using the peak year in Fig.~\ref{fig-citation} is not appropriate for all articles. On the contrary, we compute a peak year for each article.

@@

\vspace{-1ex}
\begin{small}
\begin{equation} \label{eq-infl-weights}
w(u,v)  =  \begin{cases}  \hspace{7ex} 1 & T_u <  Peak_v \\
  e^{\sigma(T_u-Peak_v)} & T_u \geq Peak_v,
\end{cases}
\end{equation}
\end{small}
%
\noindent where $T_u$ is the time of node $u$, $Peak_v$ is the peak time of node $v$ after which the impact weights of edges to $v$ decay with time, and $\sigma$ is a negative number controlling the decaying speed of the impacts.
By default, Eq.~(\ref{eq-infl-weights}) uses years as its time granularity. Note that the time decaying factor $\sigma$ is introduced to provide flexibility for TWPageRank in various applications, and its value is typically within a small interval, \eg $[-2,0]$, such that $w(u,v)$ does not decay when $\sigma=0$ and already decays more than a half per year when $\sigma=-1$.
%For the sake of completeness, we further set $w(u,v)$ to $0$ if there does not exist an edge from $u$ to $v$ in the graph.

@@

\begin{figure}[tb!]
\centering
%\includegraphics[scale=0.15]{fig/framework.eps}
\includegraphics[scale=0.15]{fig/framework-lite-2.eps}
\vspace{-1ex}
\caption{\small Ranking model \ensemblerank} \label{fig-rankmodel}
\vspace{-3ex}
\end{figure}

@@

%However, the resulting author citation graph to compute the prestige is typically too large to handle.
\markedb{To do this, an {\em author citation graph} needs to be constructed such that (a) a node represents an author, and (b) a direct edge $(s,t)$ denotes that there exist articles of author $s$ citing articles of author $t$. It is not hard to image that the number of edges in the author citation graph is much larger than the number in the citation graph, which reaches to 7.12  billion on the largest \magdata (\ie the memory cost of storage only is 57GB). It is computationally expensive to compute prestige of authors with TWPageRank on that graph.}
Hence, we evaluate the prestige of an author, by using the average prestige of all articles published by the author. Similar to the venue component, the popularity of an author is also defined as the average popularity of her/his published articles. Finally, the prestige and popularity are combined to derive the importance in the same way as the citation component.

@@

\stitle{Ranking with importance assembling}. The aforementioned importance is finally assembled to produce the final ranking, as illustrated in Fig.~\ref{fig-rankmodel}. Before assembling, each component is properly scaled such that the average importance scores of citations, venues and authors are the same.  Let the scaled importance scores of article $v$ be $R_c(v)$, $R_v(v)$, and $R_a(v)$ from the citation, venue and author components, respectively.
%
The final ranking score $R(v)$ is aggregated as follows:
